Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum

### 2015-11-13 DishReflectometry/Paper1_v0.tex
Changed 3 plots and added necessary text to the plot caption.

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In \citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \vec b, \tau )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum is detectable.

@@

where $\Phi = 2\pi\nu\Delta \tau$. The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec b, \nu)$. The corresponding instrument response may be written as,

@@

and the measured visibility spectrum, integrated over all sky would be, 
\begin{equation}\label{eqn:series1}
\vis(\vec b, \nu)  = \int I_{sky}\Sigma(\vec b, \nu) d\Omega
\end{equation}

@@

\begin{figure}[H]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/bh_vs_sq.png}
\caption{Delay plot produced for the PAPER bandwidth ($100MHz-200MHz$) by taking the Fourier transform of the measured return loss using four different window functions: Blackman-Harris, square, Hamming, and Hanning.}
\label{fig:window}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay3_window.png}
\caption{Delay plots produced using a Hamming window function for 5 different cases. Three of the cases correspond to measurements taken in Green Bank for three frequency bandwidths: $50MHz-250MHz$ (HERA bandwidth), $100MHz-200MHz$ (PAPER bandwidth), and $140MHz-160MHz$ (typical power spectrum bandwidth). Two of the cases correspond to measurements taken in 2014 of the first prototype HERA dish in Berkeley (without a feed cage). Of these, we plot data for two frequency bandwidths: $100MHz-200MHz$ (PAPER bandwidth), and $50MHz-1000MHz$ (full bandwidth used by the VNA). For the PAPER bandwidth data, we follow the same Fourier-transform analysis as the others, while the full bandwidth data is produced directly by the VNA. The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:3bands}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay_heights_paper.png}
\caption{Delay plots produced using a Hamming window function for 4 different feed heights and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:elevator}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
\caption{Delay plots produced using a Hamming window function for different lone feed configurations and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

>>>>

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In \citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum is detectable.

@@

The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec b, \nu)$. The corresponding instrument response may be written as,

@@

and the measured visibility spectrum, integrated over all sky would be, 
\begin{equation}\label{eqn:series1}
\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
\end{equation}
Corresponding delay spectrum would be, 
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
  			      & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
\end{eqnarray}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\linewidth]{plots1/delayspectrum.png}
\caption{Delay transform of the transfer function of the HERA element. The complex return loss of the element is measured between 50 to 400~MHz when the feed is kept at the focal plane of the dish at a focal height 4.5m. The delay spectrum is produced by taking the Fourier transform of the magnitude of the return loss measurement after limiting the measurements between 100 to 200~MHzusing Blackman-Harris window. The intersection of the horizontal and vertical dashed line shows the instrument performance specification as predicted by the theory of delay transform in order to detect the 21cm power spectrum.}
\label{fig:window}
\end{figure}

\begin{figure}
\centering
\includegraphics[totalheight=0.6\linewidth]{plots1/delayspectrum_feed.png}
\caption{Delay transform of the transfer function of the HERA feed element. The feed is kept on the ground downside up so that the entire radiation from the feed is radiated out. Once again, the measurement is done between 50 to 450 MHz and the delay spectrum is produced between $100-200$~MHz by using a Blackman-Harris window. The black dashed lines illustrate the instrument specification.}
\label{fig:outofthedish}
\end{figure}

@@

@@

%\begin{figure}[ht!]
%\centering
%\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
%\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights. Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
%\label{fig:elevator}
%\end{figure}

@@
